Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species

### 2015-07-31 docs/ms_sageAbundance.Rmd
fixes typo

\textit{\small{\textsuperscript{1}Department of Wildland Resources and the Ecology Center, 5230 Old Main Hill, Utah State University, Logan, Utah 84322-5230 USA; \textsuperscript{2}U.S. Geological Survey, Colorado Cooperative Fish and Wildlife Research Unit; \textsuperscript{3}Department of Fish, Wildlife, and Conservation Biology, Colorado State University; \textsuperscript{4}Department of Statistics, Colorado State University; \textsuperscript{5}Graduate Degree Program in Ecology, Colorado State University, Fort Collins, CO; \textsuperscript{6}Department of Ecosystem Science and Sustainability and Natural Resource Ecology Laboratory, Colorado State University; \textsuperscript{7}U.S. Geological Survey, Fort Collins Science Center; \textsuperscript{8}U.S. Geological Survey (USGS) Earth Resources Observation and Science (EROS) Center, Sioux Falls, SD}}

>>>>

\textit{\small{\textsuperscript{1}Department of Wildland Resources and the Ecology Center, 5230 Old Main Hill, Utah State University, Logan, Utah 84322-5230 USA}} \\*
\textit{\small{\textsuperscript{2}U.S. Geological Survey, Colorado Cooperative Fish and Wildlife Research Unit}} \\*
\textit{\small{\textsuperscript{3}Department of Fish, Wildlife, and Conservation Biology, Colorado State University}} \\*
\textit{\small{\textsuperscript{4}Department of Statistics, Colorado State University}} \\*
\textit{\small{\textsuperscript{5}Graduate Degree Program in Ecology, Colorado State University, Fort Collins, CO}} \\*
\textit{\small{\textsuperscript{6}Department of Ecosystem Science and Sustainability and Natural Resource Ecology Laboratory, Colorado State University}} \\*
\textit{\small{\textsuperscript{7}U.S. Geological Survey, Fort Collins Science Center}} \\*
\textit{\small{\textsuperscript{8}U.S. Geological Survey (USGS) Earth Resources Observation and Science (EROS) Center, Sioux Falls, SD}}
